Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2020-02-01 Tex/Old text/chapters/chapter02.tex
thesis update

\begin{itemize}
\item Standalone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid. Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting systems, solar lanterns, and solar power plants; 
\item Grid-connected systems, where the solar PV system is connected to the grid. The grid-connected system can be either a grid-tied system, which can only feed power into the grid, with the result that this system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards. Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode; 
\item Solar PV hybrid systems: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand. In this type of system, the main objective is to bring more reliability into the overall system at an affordable cost by adding one or more energy sources.
\end{itemize}

In the specific case of isolated communities, depending on the type of load, cost, resources availability, and the load requirements, standalone systems can be split into several categories, as described below. Since the goal of this Thesis is to present solutions only to isolated/ off-grid applications, on-grid or hybrid configurations are not discussed here.

@@

\subsection{Unregulated standalone PV systems with DC load }
Usually this type of system is for low power applications, as defined by \cite{Roy}. The PV system is directly connected to the load without any MPPT controller, as shown in Fig.\ref{fig:unregSPV}. At night, the system will not provide any supply because of the absence of a battery.

\begin{figure}[h]
\includegraphics[width=0.6\textwidth]{unregulatedSPV.png}
\centering
\caption{Unregulated standalone solar PV system with DC load. Source: \cite{Roy}.}
\label{fig:unregSPV}
\end{figure}

\subsection{Regulated standalone PV systems with DC load}
Similar to the unregulated standalone system with DC load, the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated in Fig.\ref{fig:regSPV1}. Usually systems with MPPT should have a battery; otherwise, the extra power will be wasted.

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV1.png}
\centering
\caption{Regulated standalone solar PV system with DC load. Source: \cite{Roy}.}
\label{fig:regSPV1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Regulated standalone systems with battery and DC load}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV2.png}
\centering
\caption{Regulated standalone solar PV system with battery and DC load. Source: \cite{Roy}.}
\label{fig:regSPV2}
\end{figure}

According to \cite{Pinho}, PV systems that are used to feed loads with low variation of consumption can be sized to operate without the controller. This is known as a self-regulated standalone PV system with battery. However, PV panel voltage must be compatible with the battery voltage. Normally, the bank of batteries is oversized in relation to the PV panel and to the load. The drawback is the operation of the batteries, normally overloaded or with excessive discharges (that can damage the batteries).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Regulated standalone systems with battery, AC load}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV3.png}
\centering
\caption{Regulated standalone PV system with battery, AC load. Source: \cite{Roy}.}
\label{fig:regSPV3}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Design and Validation of a Solar photovoltaic system}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Component models for stand-alone PV systems}
\label{model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The main purpose of this section is to describe the models for the elements of a standalone PV system: the PV generator, battery, controller, inverter, and load. The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}, from \cite{Hansen}. The modular structure facilitates the modeling of the other system structures and the replacement of elements such as a DC load instead of an AC load.

\begin{figure}[h]
\includegraphics[width=0.95\textwidth]{blockdiagramPVS}
\centering
\caption{Block diagram for the stand-alone PV system. Source: \cite{Hansen}.}
\label{fig:blockdiagram}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{PV generator (cell, module, string, and array) }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

These uncertainties lead to either over- or underestimation of energy yield from PV modules. An overestimation of up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}. The growing demand for photovoltaics technologies has led to research into the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Rajanna}, \cite{Badejani}; \cite{Yatimi}, \cite{Ferrari}, \cite{Saloux}, \cite{Hasan}, \cite{King}, \cite{Mellit}. Modeling PV modules is one of the major components responsible for proper functioning of PV systems. However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage. Therefore, perfect modeling is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.

@@

\begin{equation}
\label{eq:1diodemodel}
I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right)  \right] 
\end{equation}

@@

\begin{equation}
\label{eq:Vmderiv}
V_{m}=\dfrac{aNk_{B}T}{q} ln \left( -\dfrac{qNk_{B}T}{qI_{0}} \left( \dfrac{dI}{dV}  \right)_{V_{m}}   \right) 
\end{equation}

@@

Several models have been presented in the literature. However, regardless of the model, normally the following parameters are normally required:

\begin{itemize}
\item Nominal capacity ($ q_{m} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery, under predetermined discharge conditions.
\item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $. Obviously $ 0<SOC<1 $. If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged
\item Charge (or discharge) regime.This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). It is expressed in hours: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
\item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
\end{itemize}

The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components. Battery efficiency was described in this section, and the liability is quantified by the concept of loss of load probability (LLP). LLP is defined as the ratio between the Ampere-hour deficit and the Ampere-hour demand, both with respect to the load, over a long period of time \cite{Copetti}.

@@

The terminal voltage of the battery can be expressed in terms of its open circuit voltage and the voltage across the internal resistance of the battery \cite{Sukamongkol}, as shown by Equation 31.

Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.

@@

Most of the models created were used to simulate and optimize PV storage systems based on lead-acid batteries, the most commonly used batteries in PV applications, owing to their relative low cost and wide availability \cite{Copetti}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sizing Stand-alone Solar Photovoltaic Systems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The mathematical model presented in section~\ref{model} is important for project validation; however if an approach is used to perform the sizing of stand-alone PV systems, then the tool proposed in this thesis can perform system validation (the intended behavior), and moreover obtain optimal project sizing.

>>>>

\begin{itemize}
\item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid. Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting systems, solar lanterns, and solar power plants; 
\item Grid-connected systems, where the solar PV system is connected to the grid. The grid-connected system can be either a grid-tied system, which can only feed power into the grid, with the result that this system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards. Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode; 
\item Solar PV hybrid systems: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand. In this type of system, the main objective is to bring more reliability into the overall system at an affordable cost by adding one or more energy sources.
\end{itemize}

In the specific case of isolated communities, depending on the type of load, cost, resources availability, and the load requirements, stand-alone systems can be split into several categories, as described below. Since the goal of this Thesis is to present solutions only to isolated/ off-grid applications, on-grid or hybrid configurations are not discussed here.

@@

\subsection{Unregulated Stand-alone PV Systems With DC Load }
Usually this type of system is for low power applications, as defined by \cite{Roy}. The PV system is directly connected to the load without any MPPT controller, as shown in Fig.\ref{fig:unregSPV}. At night, the system will not provide any supply because of the absence of a battery.

\begin{figure}[h]
\includegraphics[width=0.6\textwidth]{unregulatedSPV.png}
\centering
\caption{Unregulated stand-alone solar PV system with DC load. Source: \cite{Roy}.}
\label{fig:unregSPV}
\end{figure}

\subsection{Regulated Stand-alone PV Systems With DC Load}
Similar to the unregulated stand-alone system with DC load, the main difference between this and the previous one is that this system requires a MPPT technique, as illustrated in Fig.\ref{fig:regSPV1}. Usually systems with MPPT should have a battery; otherwise, the extra power will be wasted.

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV1.png}
\centering
\caption{Regulated stand-alone solar PV system with DC load. Source: \cite{Roy}.}
\label{fig:regSPV1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Regulated Stand-alone Systems With Battery and DC load}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV2.png}
\centering
\caption{Regulated stand-alone solar PV system with battery and DC load. Source: \cite{Roy}.}
\label{fig:regSPV2}
\end{figure}

According to \cite{Pinho}, PV systems that are used to feed loads with low variation of consumption can be sized to operate without the controller. This is known as a self-regulated stand-alone PV system with battery. However, PV panel voltage must be compatible with the battery voltage. Normally, the bank of batteries is oversized in relation to the PV panel and to the load. The drawback is the operation of the batteries, normally overloaded or with excessive discharges (that can damage the batteries).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Regulated Stand-alone Systems With Battery and AC load}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV3.png}
\centering
\caption{Regulated stand-alone PV system with battery, AC load. Source: \cite{Roy}.}
\label{fig:regSPV3}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Design and Validation of a Solar PV System}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Component models for stand-alone PV systems}
\label{sec:model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The main purpose of this section is to describe the models for the elements of a stand-alone PV system: the PV generator, battery, controller, inverter, and load. The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}, from \cite{Hansen}. The modular structure facilitates the modeling of the other system structures and the replacement of elements such as a DC load instead of an AC load.

\begin{figure}[h]
\includegraphics[width=0.95\textwidth]{blockdiagramPVS2}
\centering
\caption{Block diagram for the stand-alone PV system. Source: \cite{Hansen}.}
\label{fig:blockdiagram}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{PV Generator (Cell, Module, String, and Array) }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

These uncertainties lead to either over- or underestimation of energy yield from PV modules. An overestimation of up to 40\% was reported as compared to the rated power output of PV modules \cite{Durisch}. The growing demand for photovoltaics technologies has led to research into the various aspects of its components from cell technology to the modeling, size optimization, and system performance \cite{Rajanna}, \cite{Badejani}; \cite{Yatimi}, \cite{Ferrari}, \cite{Saloux}, \cite{Hasan}, \cite{King}, \cite{Mellit}. Modeling PV modules is one of the major components responsible for proper functioning of PV systems. However, the estimation of models is affected by various intrinsic and extrinsic factors, which ultimately influence the behavior of current and voltage. Therefore, the choice of the model is essential to estimate the performance of PV modules in different environmental conditions \cite{Jakhrani}.

@@

\begin{equation}
\label{eq:1diodemodel}
I = I_{ph}-I_{D1}=I_{ph}-I_{0}\left[ exp \left( \dfrac{V}{NaV_{T}} \right) -1 \right] 
\end{equation}

@@

\begin{equation}
\label{eq:Vmderiv}
V_{m}=\dfrac{aNk_{B}T}{q} ln \left( -\dfrac{aNk_{B}T}{qI_{0}} \left( \dfrac{dI}{dV}  \right)_{V_{m}}   \right) 
\end{equation}

@@

Several models have been presented in the literature. However, regardless of the model, normally the following parameters are normally required\cite{Mellit}:

\begin{itemize}
\item Nominal capacity ($ q_{m} $), is the number of Ampere-hours ($ Ah $) that can maximally be extracted from the battery, under predetermined discharge conditions.
\item State of charge ($ SOC $), is the ratio between the present capacity and the nominal capacity, i.e., $ SOC = q/q_{max} $. Obviously $ 0<SOC<1 $. If $ SOC=1 $, then the battery is totally charged; and if $ SOC=0 $, the battery is fully discharged.
\item Charge (or discharge) regime. This parameter reflects the relationship between the nominal capacity of a battery and the current at which it is charged (or discharged). It is expressed in hours. %: for instance, discharge regime is 30h for a battery of 150 Ah that is discharged at 5A.
\item Efficiency ($\eta_{b}$), is the ratio of the charge extracted during discharge divided by the amount of the charge needed to restore the initial state of charging or discharging current. 
\item Lifetime, is the number of charge/discharge cycles the battery can sustain before losing 20\% of its nominal capacity.
\end{itemize}

The merit of a stand-alone PV system is evaluated in terms of the reliability of the electricity supply to the load and in terms of the long-term efficiency of the components. Battery efficiency was described in this section, and the reliability is quantified by the concept of loss of load probability (LLP). LLP is defined as the ratio between the Ampere-hour deficit and the Ampere-hour demand, both with respect to the load, over a long period of time \cite{Copetti}.

@@

%The terminal voltage of the battery can be expressed in terms of its open circuit voltage and the voltage across the internal resistance of the battery \cite{Sukamongkol}, as shown by Equation 31.  
%Where $ V_{b} $ is the battery terminal voltage, $ E_{oc} $ is the battery circuit voltage, $ I_{b} $ is the battery current, and $ R_{b} $ is the internal resistance of the battery.

@@

Most of the models created were used to simulate and optimize PV storage systems based on lead-acid batteries, the most commonly used batteries in developing countries, owing to their relative low cost and wide availability. % \cite{Copetti}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sizing Stand-alone Solar Photovoltaic Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The mathematical model presented in section~\ref{sec:model} is important for project validation; however if an approach is used to perform the sizing of stand-alone PV systems, then the tool proposed in this thesis can perform system validation (the intended behavior), and moreover obtain optimal project sizing.

### 2020-02-01 Tex/Old text/chapters/chapteroptimization.tex
thesis update

\section{Optimal Sizing of Solar PV Systems}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.75\columnwidth]{fig2_rev.jpg}
	\caption{CEGIS applied to PV system sizing.}
	\label{CEGISalt}
\end{figure}

@@

 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \REQUIRE weather data (temperature, solar irradiance), list of equipment (data sheet and price information), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis)
 \ENSURE FAIL with counter-example showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment available
  \STATE Initialize variables \\
  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
%  \STATE Declare list of controllers data and cost \\
%  \STATE Declare list of batteries data and cost \\
%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Declare power demand, power peak, energy consumption \\
  \STATE Declare battery autonomy, depth of discharge, AC voltage \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:opt-algorithm}
 \end{algorithm}

@@

The general assumptions for the scientific method of automated synthesis are the same presented in Chapter~\nameref{chap:methodology1}, with respect to the code in ANSI-C, to the bound $k$, to the simulation tool comparison, and to the battery state of charge.

%---------------------------------------------------------------------------
\section{Description of the case studies} 
%---------------------------------------------------------------------------

@@

%---------------------------------------------------------------------------
\section{Results}  
\label{sec:synthesisresults}
%---------------------------------------------------------------------------

@@

CPAchecker was able to synthesize optimal sizing in six 
out of the seven case studies (cases $1$ - $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes. Fig.~\ref{fig:CPAoptc1} illustrates the result of case 4 with the optimal sizing appearing on the left size as the integer $8$ for the solar panel (which is the model RSM36-6-150P from the manufacturer Risen), battery $0$ refers to the model 12MF80 of 80 Ah from Moura, charge controller $1$ refers to the model 15A-75V MPPT from Victron  Energy, and the inverter number $3$ refers to the model IP350-11 from Epever (750 W). The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, also presented in the counter-example as well, shows the number of panels and batteries and how they are connected.

@@

\begin{figure}[h]
\includegraphics[width=1.0\textwidth]{CPA_opt_c4.png}
\centering
\caption{Counter-example generated by CPAchecker after validation of case 4 (file Counterexample.html).}
\label{fig:CPAoptc1}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison between Formal Synthesis and HOMER Pro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\section{Methodology for Optimal Sizing of Solar PV Systems}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.75\columnwidth]{fig2_rev2.jpg}
	\caption{CEGIS applied to PV system sizing.}
	\label{CEGISalt}
\end{figure}

@@

 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \REQUIRE weather data (temperature, solar irradiance), list of equipment (data sheet and price information), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis)
 \ENSURE FAIL with counterexample showing the optimal sizing; SUCCESS, saying that the project has no feasible solution considering the requirements and the list of equipment available
  \STATE Initialize variables \\
  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
%  \STATE Declare list of controllers data and cost \\
%  \STATE Declare list of batteries data and cost \\
%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Declare power demand, power peak, energy consumption \\
  \STATE Declare battery autonomy, depth of discharge, AC voltage \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:opt-algorithm}
 \end{algorithm}

@@

The general assumptions for the scientific method of automated synthesis are the same presented in Section~\ref{sec:assumptions}, with respect to the code in ANSI-C, to the bound $k$, to the simulation tool comparison, and to the battery state of charge.

%---------------------------------------------------------------------------
\section{Description of the Case Studies} 
%---------------------------------------------------------------------------

@@

%---------------------------------------------------------------------------
\section{Experimental Results}  
\label{sec:synthesisresults}
%---------------------------------------------------------------------------

@@

CPAchecker was able to synthesize optimal sizing in six 
out of the seven case studies (cases $1$ - $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes. Fig.~\ref{fig:CPAoptc1} illustrates the result of case 4 with the optimal sizing appearing on the left size as the integer $8$ for the solar panel (which is the model RSM36-6-150P from the manufacturer Risen), battery $0$ refers to the model 12MF80 of 80 Ah from Moura, charge controller $1$ refers to the model 15A-75V MPPT from Victron  Energy, and the inverter number $3$ refers to the model IP350-11 from Epever (750 W). The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, also presented in the counterexample as well, shows the number of panels and batteries and how they are connected.

@@

\begin{figure}[h]
\includegraphics[width=1.0\textwidth]{CPA_opt_c4.png}
\centering
\caption{Counterexample generated by CPAchecker after validation of case 4 (file Counterexample.html).}
\label{fig:CPAoptc1}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison Between Formal Synthesis and HOMER Pro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
